A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-07-20 Answer_to_referee_report_LensingPaper.tex

\item This is an interesting paper which makes neat use of the combination of stellar
kinematics and strong lensing to investigate the mass structure of the spiral galaxy
J1331. \\\Comment{Thanks. It is a very exiting galaxy that's definitely worth exploring.}

\item The introduction could be re-written slightly to emphasise the points that the study
wants to investigate; for instance, the opening paragraph talks about the methods
used rather than the astrophysics that the study is hoping to probe. This could
probably be removed altogether, and the second paragraph promoted to the beginning. \\\Comment{That is a good point. We changed the opening paragraph to a general sentence why determining the matter distribution of galaxies is important. We mention the different methods now in the third paragraph.}

\item It would also be nice to include some more discussion of the possibility of a recent
merger in the galaxy's past in the introduction, as this is a really interesting
feature of the galaxy in question and is also a very active topic of research. \\\Comment{Good point. 1.) We added a sentence mentioning the important role of mergers in modifying the matter distribution and added some recent references. 2.) We added a short paragraph later in the introduction that points out that J1331 is a special and very interesting galaxy for researching mergers. We also explain better that this merger is one of the reasons why we especially focus on the inner regions of J1331 in our study.}

\item The manuscript in its current form is also slightly longer than necessary at certain
points: for instance, in section 3.2.1, it is not really necessary to present all
the lensing equations (e.g. the time delay, equation 7), and similarly, section
3.3.1 contains a lot of material that is implicit in Cappellari's JAM code, and
therefore does not need to be explained equation by equation here. Section 3.3.4
also rather throws the book at the NFW profile relations – it probably isn't
necessary to include equation 22. \\\Comment{We made an effort to remove unnecessary equations in Section 3.2.1, tighten the explanation of the derivation of the Jeans equations in Section 3.3.1 and 3.3.3 and removed big and clumsy mathematical expressions by referring to the explicit equations in the literature instead. In 3.3.2 we refer stronger to the changes we made to Capellari's JAM code and kept the corresponding equations. In Section 3.3.4 we moved equations that are definitions and therefore needed inline to make it shorter; we kept the concentration vs. halo mass relation (former equation 22) and explicitely mention that we will use this later as a prior in our modelling. In general we include a lot of equations and a substantial theory introduction because it is a paper that is potentially interesting for two communities, the lensing and the dynamics community. We wanted to make the paper understandable for both.}

@@

\item From a scientific perspective, in section 4.3.3, the authors comment that the
varying M/L JAM model is unable to reproduce the dynamics when M/L is forced to be
always rising as a function of radius, but it would be interesting to see if the
model could be improved by removing this constraint. Perhaps the authors could add
such a model to this section, or else comment on why they do not attempt it. \\\Comment{We have indeed tried a ``mass-follows-light'' JAM model with constant anisotropy and free M/L profile early on in our investigations of J1331. This was unsuccessful to a degree that showing the result in the paper would not be reasonable.  The way how we can generate variable M/L profiles with our MGE mass model is restricted. We have 6 data points and 5 fit M/L parameter within 5 arcsec. This lead to an over-fitting in the inner regions where most of the Gaussians are, while not having enough flexibility at larger radii. (We added a sentence mentioning that in the paper.) The resulting profile was very wiggly, difficult to interpret and most likely unphysical.  As we lay out in the discussion, constraints on a varying stellar M/L ratio should be motivated by stellar population analysis in the future.}

\item In section 4.4.1, the NFW profile is fitted only to the inner data, and then is
shown to not provide a good model for the data beyond that point. This is not
entirely surprising, given that the outer data were not used to constrain the model!
What happens if the NFW profile is fitted to both small- and large- radius data at
once? (Perhaps it is impossible to find a good NFW model across the whole radius
range, but if this is the case, then it should be stated.) \\\Comment{Yes, you are completely right. Our initial tests tried of course to fit the whole range of data, but failed. The problem is that we were never able to fit both the central $v_\text{rms}$ dip and the dip around $R'\sim 6''$ with any of the models we tried. If you think this is frustrating, we definitely feel the same way. Our best explanation was, that the spiral arms do weird things to the kinematics around $R'\sim 5-7''$ that cannot be captured by the axisymmtric Jeans models. In this region our MGE models also were not a good fit to the galaxy anymore. Considering also that there are other studies focussing on the outer regions and the counter-rotating core is the most interesting feature, we decided to focus our efforts on the inner regions and try to explain the central kinematics only. We added however a small new section 4.4.4 that discusses that and why modelling attempts to the whole data range fail and what possible next modelling steps should be.}

\item The discussion section is too non-committal and speculative in parts. For instance,
in section 5.1, the M/Ls inferred from a number of the different models are compared
with M/Ls from the literature, but the authors do not make any value judgement
between the different models to come to any firmer conclusions about what they
believe the most convincing description of the IMF to be. At the moment, this
section seems to just be trying to show that their various models can be made to
agree with previous models from the literature, but it would be much more
interesting if some attempt could be made to resolve all the different models (both
in this paper and in previous works) or at least present them in a more coherent
framework, to try to come up with a better picture of the nature of J1331's IMF. \\\Comment{This is a valid point of criticism. We thought again about the different models and indications for different IMFs that we collected and came to the conclusion that an IMF slightly less bottom-beavy than the Salpeter IMF is the most likely model for J1331's bulge. We tried to give Section 5.2 (former 5.1) more structure and tweaked the discussion to present arguments for $\Upsilon_{I,*} \sim 4.2$ and and to argue against the alternative models.\\We also moved the section that discusses J1331's merger history to the beginning to the discussion section, focussed more on what the merger could have done to J1331's mass distribution and less on modelling failures. All following sections use the background information about mergers to discuss our models.\\Our scientific honesty is however, that without further data, we cannot be more commital and some of our statements have to stay in the "speculation regime".}

\item In Section 5.2, the authors could make suggestions for what might be causing the two
$v_{rms}$ dips. Currently, they just state what cannot be the cause, but do not make any
more convincing suggestions – e.g. could it be associated with the possible recent
merger that is explored in Section 5.3? It would be more satisfying if some
suggestions like this could be put forward. \\\Comment{Good point. We admit that the text was formulated a bit too negative, and that we can do better in explaining J1331 based on our models than just ruling out things. Also, some of the effects that mergers can have on galaxies \emph{could}, if they occured in J1331, actually explain some of the peculiar kinematic features of J1331. We tried to re-formulate section 5.3 (former 5.2) and discuss several aspects of the kinematics with respect to the merger history.}

\item While the use of English is impressive given that it is not the main author's mother
tongue, I would also recommend giving the manuscript to a native speaker to correct
the number of grammatical errors that remain. \\\Comment{One of the authors is a native speaker and he had a look at the language again. We corrected everything he thought should be corrected. Hopefully it is fine now.}

### 2016-07-20 revised_version_(4.02)_16-07-20/Trick_J1331_Modelling_revised.tex
Paper is re-submitted.

\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\Wilma}[1]{\textcolor{Magenta}{#1}}
\newcommand{\Glenn}[1]{\textcolor{Green}{#1}}
\newcommand{\Aaron}[1]{\textcolor{Blue}{#1}}

\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\NOTE}[1]{\textcolor{Cyan}{#1}}
\newcommand{\NEW}[1]{\textcolor{ForestGreen}{#1}}
%\newcommand{\OLD}[1]{\textcolor{Red}{#1}}
\newcommand{\OLD}[1]{}

@@

%--------------------------------------------
\begin{abstract}
We investigate the matter distribution of a spiral galaxy with \NEW{a} counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \OLD{\cdot}\NEW{\times} 10^{10} \text{M}_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
\end{abstract}
%--------------------------------------------

@@

%--------------------------------------------
\NEW{Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.}

\OLD{Gravitational lensing and dynamical modelling provide independent constraints on the mass distribution of galaxies. Combining them allows for valuable cross-checking opportunities to disentangle the galactic stellar and dark matter (DM) content.}

Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{1996ApJ...462..563N}. However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}). This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}). \NEW{Especially the influence of mergers on the DM and baryonic structure of galaxies is currently an active field of research (e.g., \citealt{2009ApJ...697L..38J,2010ApJ...712...88L,2012MNRAS.425.3119H,2015MNRAS.453.2447D}).}

\OLD{Determining the overall mass distribution in massive galaxies and separating the DM from the stellar mass components is therefore a crucial step in better understanding the structure and formation of galaxies and nature of DM.}

\NEW{The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling. Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content.} Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images. This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).

@@

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to \OLD{find}\NEW{finding} and \OLD{investigate}\NEW{investigating} spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured. By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.

@@

\NEW{J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive spiral galaxy. This requires in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.}

\NEW{J1331 has already been the subject of several studies:} \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge. The lensing properties of J1331 were first analysed by \citet{SWELLSIII}. \citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.

\OLD{The goal of this work is to complement the previous studies of J1331 by an in-depth analysis of the matter distribution in J1331's inner regions.}\NEW{The goal of this work is now the in-depth analysis of the matter distribution in J1331's inner regions. This will complement the previous studies of J1331 and is an important step in understanding J1331's merger-modified mass structure.} We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}. We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core. \OLD{Ideally, this work on J1331 could also help understanding how mergers modify the mass distribution of a galaxy.}

@@

%--------------------------------------------
J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside \NEW{the projected radius on the sky} $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$. \NEW{We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.}
%--------------------------------------------

@@

%--------------------------------------------
We use HST imaging of J1331 by \citet{SWELLSI}. They \OLD{performed}\NEW{obtained} high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
%--------------------------------------------

@@

Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore. We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} \OLD{\geq}\NEW{=} 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic\OLD{, to} \NEW{and} 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $\OLD{i}\NEW{inc}$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{\NEW{$(R,z)$ are cylindrical coordinates aligned with the galactic plane. The primed $(R',z')$ denote polar coordinates on the plane of the sky.}} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 \OLD{i}\NEW{(inc)}}{\sin^2 \OLD{i}\NEW{(inc)}}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

%--------------------------------------------
A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}). The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$. The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
\begin{equation}
\psi(\vect{\theta}) \OLD{:=}\NEW{\equiv} \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
\end{equation}
where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
\begin{equation}
\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vect{\theta}_i = (x_i',y_i')$. The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.

\OLD{The total time delay of a deflected light path through $\vect{\theta}$ with respect to the unperturbed light path is given by 
\begin{equation}
\Delta t(\vect{\theta}) = \frac{(1+z_d)}{c} \frac{D_\text{d} D_\text{s}}{D_\text{ds}} \left[ \frac 12 (\vect{\theta} - \vect{\beta})^2 - \psi(\vect{\theta})\right]. \label{eq:timedelay}
\end{equation}
 According to Fermat's principle the image positions will be observed at the extrema of $\Delta t(\vect{\theta})$.}

The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position\OLD{. It also describes}\NEW{,} the distortion of the image shape for an extended source and its magnification \OLD{$\mu$ due to lensing according to}\NEW{$\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$}.
\OLD{$$\mu \equiv \frac{\text{image area}}{\text{source area}} = \det \mathscr{M}.$$}
Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves. The corresponding lines in the source plane are called caustics. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.

@@

%--------------------------------------------
\OLD{JAM modelling assumes galaxies to be (i) collisionless (i.e., the collisionless Boltzmann equation for the distribution function $f(\vect{x},\vect{v},t)$ has to be satisfied, $\frac{\diff f(\vect{x},\vect{v},t)}{\diff t} = 0$), (ii) in a steady state ($\frac{\partial}{\partial t} = 0$), (iii) axisymmetric (best described in cylindrical coordinates $(R,z,\phi)$ and $\frac{\partial}{\partial \phi} = 0$). From this follow the axisymmetric Jeans equations as the vector-valued first moment of the Boltzmann equation, i.e.,
\begin{equation*}
\int \vect{v} \frac{\diff f}{\diff t} \Diff3 v = 0.
\end{equation*}}
\NEW{JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric. With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \citet{2008gady.book.....B}). The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the number density of (stellar) tracers $n(\vect{x})$, and the galaxy's gravitational potential $\Phi(\vect{x})$ generated by the mass density $\rho(\vect{x})$.}

To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made. We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$. Secondly, we assume a constant ratio between the radial and vertical second velocity moments, 
\begin{equation}
\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle, \label{eq:bz}
\end{equation}
where $\beta_z$ is the velocity anisotropy parameter. \OLD{This reduces the Jeans equations to two equations for $\langle v_z^2 \rangle$ and $\langle v_\phi^2 \rangle$ which can be solved by means of one integration,
\begin{eqnarray}
n \langle v_z^2 \rangle (R,z) &=& \int_0^\infty n \frac{\partial \Phi}{\partial z} \diff z \label{eq:Jeans1}\\
n \langle v_\phi^2 \rangle (R,z) &=& R \frac{\partial}{\partial R} \left( \frac{n \langle v_z^2 \rangle}{1-\beta_z} \right) + \frac{n \langle v_z^2 \rangle}{1 - \beta_z} + R n \frac{\partial \Phi}{\partial R},\label{eq:Jeans2}
\end{eqnarray}
where $n(\vect{x}) \equiv \int f(\vect{x},\vect{v}) \Diff3 v$ is the number density of (stellar) tracers and $\Phi(\vect{x})$ the galaxy's gravitational potential generated by the mass density $\rho(\vect{x})$.}

>>>>

@@

%--------------------------------------------
\begin{abstract}
We investigate the matter distribution of a spiral galaxy with a counter-rotating stellar core, SDSS J1331+3628 (J1331), independently with gravitational lensing and stellar dynamical modelling. By fitting a gravitational potential model to a quadruplet of lensing images around J1331's bulge, we tightly constrain the mass inside the Einstein radius $R_\text{ein}=(0.91\pm0.02)''(\simeq1.83\pm0.04~\text{kpc})$ to within 4\%: $M_\text{ein} = (7.8\pm0.3) \times 10^{10} \text{M}_\odot$. We model observed long-slit major axis stellar kinematics in J1331's central regions by finding Multi-Gaussian Expansion (MGE) models for the stellar and dark matter distribution that solve the axisymmetric Jeans equations. The lens and dynamical model are independently derived, but in very good agreement with each other around $\sim R_\text{ein}$. We find that J1331's center requires a steep total mass-to-light ratio gradient. A dynamical model including a NFW halo (with virial velocity $v_{200} \simeq 240 \pm 40~\text{km s}^{-1}$ and concentration $c_{200} \simeq 8 \pm 2$) and moderate tangential velocity anisotropy ($\beta_z \simeq -0.4 \pm 0.1$) can reproduce the signatures of J1331's counter-rotating core and predict the stellar and gas rotation curve at larger radii. However, our models do not agree with the observed velocity dispersion at large radii. We speculate that the reason could be a non-trivial change in structure and kinematics due to a possible merger event in J1331's recent past.
\end{abstract}
%--------------------------------------------

@@

%--------------------------------------------
Determining the overall mass distribution of galaxies and separating the dark matter (DM) from the stellar mass components is a crucial step in better understanding the structure and formation of galaxies and the nature of DM.

Cosmological simulations suggest that cold DM forms cuspy halos following a Navarro-Frenk-White (NFW) profile \citep{1996ApJ...462..563N}. However, the existence of central DM density cusps in massive galaxies depends strongly on the stellar mass-to-light ratio (e.g., \citealt{2011MNRAS.416..322D}) and DM dominated dwarf galaxies even favour DM halos with cores (e.g., \citealt{1994Natur.370..629M,2001ApJ...552L..23D}). This discrepancy, known as the core-cusp problem, might be resolved by galaxy formation processes such as mergers and outflows (e.g., \citealt{2001ApJ...560..636E,2012MNRAS.421.3464P}). Especially the influence of mergers on the DM and baryonic structure of galaxies is currently an active field of research (e.g., \citealt{2009ApJ...697L..38J,2010ApJ...712...88L,2012MNRAS.425.3119H,2015MNRAS.453.2447D}).

The mass distribution of massive galaxies can be measured in completely independent fashions by gravitational lensing and dynamical modelling. Combining these two methods allows for valuable cross-checking opportunities to disentangle the galactic stellar and DM content. Massive galaxies can act as gravitational lenses, deflect the light of background sources and give rise to multiple images. This strong gravitational lensing tightly constrains the projected total mass of the lens galaxy inside $\sim 1''$ (e.g., \citealt{2010ARA&A..48...87T}).

@@

The Sloan WFC Edge-on Late-type Lens Survey (SWELLS, WFC = Wide field camera) \citep{SWELLSI,SWELLSII,SWELLSIII,SWELLSIV,SWELLSV,SWELLSVI} is dedicated to finding and investigating spiral galaxies, which are (i) strong gravitational lenses and (ii) observed almost edge-on, such that rotation curves can be easily measured. By combining lensing and dynamical modelling, degeneracies inherent in both methods can be broken.

@@

J1331 is therefore of special interest and a convenient candidate to investigate observationally if and how a merger might have modified the DM and stellar distribution of a massive spiral galaxy. This requires in particular a precise disentanglement of stellar and DM components in the galaxy's inner regions.

J1331 has already been the subject of several studies: \citet{SWELLSI} confirmed that J1331 is a strong gravitational lens, measured its apparent brightness and estimated the stellar masses of disk and bulge. The lensing properties of J1331 were first analysed by \citet{SWELLSIII}. \citet{SWELLSV} measured the gas and stellar kinematics along the major axis and deduced J1331's mass profile from the gas rotation curve at large radii and total mass inside the Einstein radius from gravitational lensing, focusing mostly on the outer regions of J1331.

The goal of this work is now the in-depth analysis of the matter distribution in J1331's inner regions. This will complement the previous studies of J1331 and is an important step in understanding J1331's merger-modified mass structure. We use stellar dynamical modelling in addition to lensing constraints, similar to a study of the Einstein Cross by \citet{GlennEC}. We attempt to disentangle the stellar and DM components and test if employed axisymmetric Jeans models work also in the presence of a counter-rotating core.

@@

%--------------------------------------------
J1331 is located at right ascension = 202.91800$^\circ$ and declination = 36.46999$^\circ$ (epoch J2000). \citet{SWELLSI} found from SDSS spectra that J1331 has two redshifts inside the projected radius on the sky $R'=1''$: J1331 itself has $z_d = 0.113$ and $z_s = 0.254$ is the redshift of the lensed background source \citep{SWELLSIII}. According to the WMAP5 cosmology \citep{WMAP5cosm}, J1331 has an angular diameter distance of 414 Mpc, which translates into a transverse scaling of $1'' \hat{=} 2.01~\text{kpc}$. We summarize all galaxy parameters also in Table \ref{tab:galaxyparameters}.
%--------------------------------------------

@@

%--------------------------------------------
We use HST imaging of J1331 by \citet{SWELLSI}. They obtained high resolution imaging with the Hubble Space Telescope's (HST) Wide-Field Planetary Camera 2 (WFPC2) and its WF3 CCD chip. The images are a combination of four exposures with each an exposure time of $400~\text{sec}$ and were drizzled to a pixel scale of 1 pixel = $0.05''$. In particular, we use the images in the filters F450W, to identify the positions of the bluish lensing images, and F814W (I-band) to create a surface brightness model of the reddish bulge.
%--------------------------------------------

@@

Inside of $\sim 4''$ the data appears to be symmetric; outside of it the data suggests that the assumption of axisymmetry seems not to be valid anymore. We subtract $2.3~\text{km s}^{-1}$ from $v_\text{rot}$ to ensure $v_\text{rot}(R'=0) \sim 0$ as a possible correction term for a misjudgement of the systemic velocity. We also symmetrize the data within $4''$ and asign a minimum error of $\delta v_\text{rms} = 5~\text{km s}^{-1}$ to the $v_\text{rms}$ data. In our dynamical Jeans modelling approach, which is based on the assumption of axisymmetry, only stellar kinematics with either $R'  \lesssim 3.5''$ or $R' \lesssim 4''$ are used. Another reason to restrict the modelling to the bulge region is that our surface brightness model (Table \ref{tab:MGEF814W} and Figure \ref{fig:MGEinnerRegions}) is only a good representation of J1331's F814W light distribution inside $\sim 5''$.
%--------------------------------------------

@@

%--------------------------------------------
$I(R',\theta')$ describes the intrinsic and 2D projected light distribution or surface density of the galaxy. Under the assumption that the galaxy is oblate and axisymmetric, and given the inclination angle $inc$ of the galaxy with respect to the observer, MGEs allow an analytic deprojection of the 2-dimensional MGE to get a 3-dimensional axisymmetric light distribution or density $\nu(R,z)$ for the galaxy,
\begin{equation}
\nu(R,z) = \sum_i \nu_{0,i} \exp \left[-\frac{1}{2\sigma_i}\left(R^2 + \frac{z^2}{q_i^2} \right) \right], \label{eq:deprojMGE}
\end{equation}
where $R$ is the distance from the galaxy's short axis and $z$ the height above the galactic plane.\footnote{$(R,z)$ are cylindrical coordinates aligned with the galactic plane. The primed $(R',z')$ denote polar coordinates on the plane of the sky.} The flattening $q_i$ of each axisymmetric 3D Gaussian and its central density $\nu_{0,i}$ follow from the observed 2D axis ratio $q'_i$ and surface density $I_{0,i}$ as
\begin{eqnarray}
q_i^2 &=& \frac{q_i'^2 - \cos^2 (inc)}{\sin^2 (inc)}\\
\nu_{0,i} &=& \frac{q_i' I_{0,i}}{q_i \sqrt{2 \pi \sigma_i^2}}.
\end{eqnarray}
%--------------------------------------------

@@

%--------------------------------------------
A gravitational lens is a mass distribution whose gravitational potential $\Phi$ acts as a lens for light coming from a source positioned somewhere on a plane behind the lens. We summarize the basic formalism (see also \citealt{1992grle.book.....S,1996astro.ph..6001N,2006glsw.conf....1S,2006glsw.conf...91K,2010ARA&A..48...87T}). The angular diameter distance from the observer to the lens is $D_\text{d}$, to the source plane $D_\text{s}$, and the distance between the lens and source plane is $D_\text{ds}$. The deflection potential of the lens is its potential projected along the line of sight $z'$ and rescaled to
\begin{equation}
\psi(\vect{\theta}) \equiv \frac{D_\text{ds}}{D_\text{d} D_\text{s}} \frac{2}{c^2} \int \Phi(\vect{r}=D_\text{d} \vect{\theta},z') {\ \mathrm d} z', \label{eq:psidef}
\end{equation}
where $\vect{\theta}\equiv(x',y')$ is a 2-dimensional vector on the plane of the sky. The light from the source at $\vect{\beta} \equiv (x_s',y_s')$ is deflected according to the lens equation
\begin{equation}
\vect{\beta} = \vect{\theta}_i - \left.\vect{\nabla}_\theta \psi(\vect{\theta})\right|_{\vect{\theta}_i} \label{eq:lenseqpot}
\end{equation}
into an image $\vect{\theta}_i = (x_i',y_i')$. The gradient of the deflection potential, $\vect{\nabla}_\theta \psi(\vect{\theta})$, is equal to the angle by which the light is deflected multiplied by $D_\text{ds}/D_\text{s}$.

The inverse magnification tensor
\begin{equation}
\mathscr{M}^{-1} \equiv \frac{\partial \vect{\beta}}{\partial \vect{\theta}} \overset{(\ref{eq:lenseqpot})}{=} \left(\delta_{ij} - \frac{\partial^2 \psi}{\partial \theta_i \partial \theta_j} \right)\label{eq:magnificationtensor}
\end{equation}
describes how the source position changes with image position, the distortion of the image shape for an extended source and its magnification $\mu \equiv \text{image area}/\text{source area} = \det \mathscr{M}$. Lines in the image plane for which the magnification becomes infinite, i.e., $\det \mathscr{M}^{-1} = 0$, are called critical curves. The corresponding lines in the source plane are called caustics. The position of the source with respect to the caustic detemines the number of images and their configuration and shape with respect to each other.

@@

%--------------------------------------------
JAM modelling assumes galaxies to be (i) collisionless, (ii) in a steady state and (iii) axisymmetric. With these assumptions the axisymmetric Jeans equations follow from the vector-valued first moment of the collisionless Boltzmann equation (see Equations (4.221)-(4.222) in \citet{2008gady.book.....B}). The Jeans equations are functions of the second velocity moments $\langle v_i v_j\rangle$ (with $i,j\in(R,z,\phi)$), the number density of (stellar) tracers $n(\vect{x})$, and the galaxy's gravitational potential $\Phi(\vect{x})$ generated by the mass density $\rho(\vect{x})$.

To be able to solve the Jeans equations, additional assumptions about the velocity ellipsoid tensor $\langle v_i v_j\rangle$ have to be made. We follow \citet{Cap08} and assume firstly that the galaxy's velocity ellipsoid is aligned with the cylindrical coordinate system, i.e., $\langle v_R v_z\rangle = \langle v_z v_\phi \rangle = \langle v_\phi v_R \rangle = 0$. Secondly, we assume a constant ratio between the radial and vertical second velocity moments, 
\begin{equation}
\beta_z \equiv 1 - \langle v_z^2 \rangle / \langle v_R^2\rangle, \label{eq:bz}
\end{equation}
where $\beta_z$ is the velocity anisotropy parameter.

The JAM modelling approach by \citet{Cap08} expresses the tracer and mass density in terms of MGEs (see also \citealt{1994A&A...285..723E}). The tracer density $n(\vect{x})$ is assumed to be proportional to the observed and deprojected brightness distribution $\nu(R,z)$ in Equation \eqref{eq:deprojMGE}. The mass density $\rho(R,z)$ can consist of several sets of MGEs, describing stellar and DM components. The MGE for $\Phi(R,z)$ is generated from the mass density MGE by integrating the Poisson equation \citep{1994A&A...285..723E}.

In this way one can now calculate an unambiguous model prediction for the velocity dispersion tensor $\langle v_i v_j \rangle(R,z) = \langle v_i^2 \rangle(R,z)$ (with $i,j \in \{ R,\phi, z\}$ and $\langle v_i v_j \rangle=0$ if $i\neq j$). To compare it with observations, $\langle v_i^2 \rangle(R,z)$ has to be rotated by the inclination angle $inc$ to the coordinate system of the observer; $(x',y')$ is the plane of the sky and $z'$ the line-of-sight, where $x'$ is alinged with the galaxy's major axis. Taking a light-weighted projection along the line-of-sight gives a model prediction for the line-of-sight velocity second moment $\langle v_\text{los}^2\rangle(x',y')$, which is comparable to actual spectroscopic measurements of the second velocity moment. Details of the derivation of $\langle v_\text{los}^2\rangle(x',y')$ from the Jeans equations using the MGE formalism are laid out in \citet{Cap08} and in the appendix of \citet{GlennEC}. The result for $\langle v_\text{los}^2\rangle(x',y')$ in particular is given in Equation (28) and Equation (A18), respectively.
